---
title: "R Notebook"
output: html_notebook
---

Conflating some of the crimes categories into others, as some happen very rarely and take space in the UI

Loading libraries we plan on using
```{r}
library(chron) # for dealing with chronological objects
library(magrittr) # pipe operator
library(plyr) # rename
library(readr)# read_csv(), ~3x faster than read.csv()
```

Read the file created with munging1.Rmd
```{r}
start <- Sys.time()
chicago_crimes <- read_csv("chicago_crimes.csv")
chicago_crimes$categories %>% table() %>% sort()
Sys.time() - start
```

We can see only ONE case of Domestic Violence (?) so I will conflate it into "OTHER OFFENSE". We can do similarly with the "NON-CRIMINAL" catgories (3 of them), as well as the "RITUALISM" and "CONCEALED CARRY LICENSE VIOLATION" categories. The "OTHER NARCOTIC VALUATION" can be conflated with "NARCOTICS".

```{r}
chicago_crimes[chicago_crimes$categories == "DOMESTIC VIOLENCE",]$categories <- "OTHER OFFENSE"
chicago_crimes[chicago_crimes$categories == "NON-CRIMINAL (SUBJECT SPECIFIED)",]$categories <- "OTHER OFFENSE"
chicago_crimes[chicago_crimes$categories == "NON - CRIMINAL",]$categories <- "OTHER OFFENSE"
chicago_crimes[chicago_crimes$categories == "NON-CRIMINAL",]$categories <- "OTHER OFFENSE"
chicago_crimes[chicago_crimes$categories == "RITUALISM",]$categories <- "OTHER OFFENSE"
chicago_crimes[chicago_crimes$categories == "CONCEALED CARRY LICENSE VIOLATION",]$categories <- "OTHER OFFENSE"
chicago_crimes[chicago_crimes$categories == "OTHER NARCOTIC VIOLATION",]$categories <- "NARCOTICS"

#Check:
chicago_crimes$categories %>% table() %>% sort()
```

Write to file:
```{r}
write_csv(chicago_crimes, "chicago_crimes_2017_0220.csv")
```

Write the files
```{r}
start <- Sys.time()
for(year in c(2001:2017)) {
  crimes <- chicago_crimes[chicago_crimes$year == as.character(year),]
  write_csv(as.data.frame(crimes), paste("crimes_", as.character(year), ".csv", sep=""))
}
Sys.time() - start
```